### 2022-05-15 draft.tex
rough structure

\pagenumbering{arabic}
\setcounter{page}{3}
\section{Introduction}

	\newpage
\section{History}

\subsection{Disovery of Genes}
While initial speculation about genetics dates back to Hippocrates and Aristotle, who developed theories to explain inheritance\cite{mayr}, it was not until 1856 when Gregor Mendel experimented with cross breeding numerous pea plants to discover patterns in attribute inheritance\cite{mendel}, not knowing his actions would plant a seed within biology that would soon bloom to disrupt areas of daily life far beyond the bounds of science.
The groundbreaking discovery he made was that the phenotype of a given plant is not a mere blend of the visible attributes its parents held, but rather a seemingly random combination of the genetic lineage, meaning even attributes last observed several generations ago could be present\cite{mendel}.
Mendels work lead to a deeper understanding of the underlying genotype, dominant and recessive genes and was fundamental to the development of the techniques discussed in this paper.

@@

\subsection{Genome Analysis}
Necessary for the manipulation of genetic material is first understanding DNA and its function, which this paper will focus primarily on.
This breaks down into two steps.
Firstly DNA Sequencing, which means simply determining the sequence of DNA base pairs without interpretation. It enables the diagnosis of point mutations and similarity measurement, as well as forming the base for further analysis.
Secondly Genome-wide association studies (GWAS), which aim to map genetic variants to observable traits.

\section{Medical Sector}

@@

	\newpage
\pagenumbering{gobble}
\begin{thebibliography}{99}

@@

>>>>

\pagenumbering{arabic}
\setcounter{page}{3}

	\newpage
\section{Historical and Technical Introduction}

\subsection{Discovery of Genes}
While initial speculation about genetics dates back to Hippocrates and Aristotle, who developed theories to explain inheritance\cite{mayr}, it was not until 1856 when Gregor Mendel experimented with cross breeding numerous pea plants to discover patterns in attribute inheritance\cite{mendel}, not knowing his actions would plant a seed within biology that would soon bloom to disrupt areas of daily life far beyond the bounds of science.
The groundbreaking discovery he made was that the phenotype of a given plant is not a mere blend of the visible attributes its parents held, but rather a seemingly random combination of the genetic lineage, meaning even attributes last observed several generations ago could be present\cite{mendel}.
Mendels work lead to a deeper understanding of the underlying genotype, dominant and recessive genes and was fundamental to the development of the techniques discussed in this paper.

@@

\subsection{Genome Analysis}
Necessary for the manipulation of genetic material is first understanding DNA, its function and effects of deviation from the norm, which this paper will focus primarily on.
Fundamental understanding breaks down into two steps.
Firstly DNA Sequencing, which means simply determining the sequence of DNA base pairs without interpretation. It enables the diagnosis of point mutations and similarity measurement, as well as forming the base for further analysis.
Secondly gene association studies, which aim to map genetic variants to observable traits and come in two varieties. 
Genome-wide association studies (GWAS) hope to uncover any correlation between strings of DNA and phenotype, while specific genetic association or gene linkage studies focus on specific variants of a gene (alleles) and examine whether they frequently cooccur with disease\cite{gwas}.

\section{Who Are You}

\subsection{DNA and Identity}

\section{What Have You Done}

\subsection{Forensics}
The controversy around privacy versus surveillance applies to genome analysis as much as to any sensitive technology.

\section{What Does Your Future Look Like}

\subsection{Medical Sector}

\subsection{Insurance}

\section{Consequences for Society: Social Compatibility}

\subsection{Eugenics}

\subsection{Totalitarian Police State}

@@

\pagenumbering{gobble}
\begin{thebibliography}{99}

@@

\bibitem{gwas} 
\textbf{GWA (genome-wide association, GWAS)} (Springer Dordrecht, 2008)
